Describing the C-Space of Asynchronous Periodic Task Systems using Definitive Idle Times

### 2013-07-29 dit-paper_ieee.tex
Corrected matrix size

(Remarque : Sans appliquer le simplexe ou un truc comme ça, si un DIT existe on divisera toujours par exactement 4 le nombre de contraintes ??)

@@

\begin{figure}[h]
$$z = \max C \, X$$
s.t.
\[
\begin{array}{rccc}
	A & X &\leq & B \\
	C & X &\leq & d + 1
\end{array}
\]
with
\[
	\begin{array}{ccc}
		A & : & [k,n] \text{ matrix}\\
		B & : & [1,n] \text{ matrix}\\
		C & : & [n,1] \text{ matrix}\\
		X & : & [1,n] \text{ matrix}\\
		d & : & \text{integer}
	\end{array}
\]
\caption{Redundancy of $CX \leq d$ w.r.t. $A X \leq B$ as an ILP}
\end{figure}

@@

Such a linear problem can be solved by the simplex algorithm. However, in our case the problem is not exactly the same as we have a set of constraints and we want to find all redundant constraints within. A naive method would be to test each constraint against all the others. We present a similar method with an efficient preprocessing when most constraints are redundant in Algorithm \ref{alg:prunRedun}.\\

@@

To summarize, we first reduced the number of constraint from every possible interval $[t_1, t_2]$ to only the interval where $t_1$ is an arrival and $t_2$ is a deadline between $[t_d, t_d + H]$ if $t_d$ exists, or between $[O_{max}, O_{max} + 2H]$ otherwise. After this correct but not efficient description of the C-SPACE, a linear integer approach removes the remaining redundancies. Note that

@@

The FPDIT happens at $t=15$ and we have $H = 15$. The study interval using the FPDIT is thus $[15, 30]$, which contains 11 intervals $[a,d]$ with $a$ being the arrival of a job, $d$ being the deadline of a job, and $15 \leqslant a < d \leqslant 30$. Those intervals are
$[15, 17]$, $[15, 22]$, $[15, 27]$, $[15, 30]$, $[20, 22]$, $[20, 27]$, $[20, 30]$, $[23, 27]$, $[23, 30]$, $[25, 27]$ and $[25, 30]$. For comparison, the more pessimistic study interval is $[8, 38]$ which yields 57 intervals.\\

>>>>

(Remarque : Avec seulement cette méthode, si un DIT existe on divisera toujours par exactement 4 le nombre de contraintes par rapport à $O_{max} + 2H$)

@@

\begin{figure}[h]
$$z = \max C \, X$$
s.t.
\[
\begin{array}{rccc}
	A & X &\leq & B \\
	C & X &\leq & d + 1
\end{array}
\]
with
\[
	\begin{array}{ccc}
		A & : & [n,k] \text{ matrix}\\
		B & : & [n,1] \text{ matrix}\\
		C & : & [n,1] \text{ matrix}\\
		X & : & [1,n] \text{ matrix}\\
		d & : & \text{integer}
	\end{array}
\]
\caption{Redundancy of $CX \leq d$ w.r.t. $A X \leq B$ as an ILP}
\end{figure}

@@

Such a linear problem can be solved by e.g. the simplex algorithm and a branch-and-cut approach. However, in our case the problem is not exactly the same as we have a set of constraints and we want to find all redundant constraints within. A naive method would be to test each constraint against all the others. We present a similar method with an efficient preprocessing when most constraints are redundant in Algorithm \ref{alg:prunRedun}.\\

@@

To summarize, we first reduced the number of constraint from every possible interval $[t_1, t_2]$ to only the interval where $t_1$ is an arrival and $t_2$ is a deadline between $[t_d, t_d + H]$ if $t_d$ exists, or between $[O_{max}, O_{max} + 2H]$ otherwise. After this correct but not efficient description of the C-SPACE, a linear integer approach removes the remaining redundancies.

@@

The FPDIT happens at $t=15$ and we have $H = 15$. The study interval using the FPDIT is thus $[15, 30]$, which contains 11 intervals $[a,d]$ with $a$ being the arrival of a job, $d$ being the deadline of a job, and $15 \leqslant a < d \leqslant 30$. Those intervals are
$[15, 17]$, $[15, 22]$, $[15, 27]$, $[15, 30]$, $[20, 22]$, $[20, 27]$, $[20, 30]$, $[23, 27]$, $[23, 30]$, $[25, 27]$ and $[25, 30]$. For comparison, the original study interval of $[O_{max}, O_{max} + 2H]$ is $[8, 38]$ which yields 57 intervals.\\
